---
title: "Data"
output: github_document
---

```{r, echo=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
require(knitr)
setwd('/Users/francesco/public_git/ScrapeOpen/sistat.istat.it/')
csv_files <- list.files(pattern = "csv$")
```

This document describes the tables produced from scraping *comune* variations from sistat.istat.it.

```{r}
version <- "20190601"
```


## Variables

* `sistat_id`: a *comune* unique ID within the dataset
* `?(*_)istat_cod`: reference to *comune* the ISTAT code.
* `event_num`: the unique ID of an event within the dataset.

## Tables

### Comuni

This table contains one record for each *comune* describes in the dataset.

```{r}
filename <- sprintf("open_csv_%s_comuni.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```

### Comuni variations

This table contains one record for each variation associated with a *comune*. A *comune* with no variation is not present in this table (I think...).

```{r}
filename <- sprintf("open_csv_%s_comuni_variations.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```

### Events

This table details the variation events and the scope of the variation events described in the dataset.

```{r}
filename <- sprintf("open_csv_%s_events.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 3),], row.names = FALSE)
```

### Event: change code

This table details variations in the ISTAT code.

```{r}
filename <- sprintf("open_csv_%s_event_change_code.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```

### Event: change name

This table details variations in the name. 

```{r}
filename <- sprintf("open_csv_%s_event_change_name.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```

### Event: change part of

This table details variations in hierarchical relations (when a *comune* change provice).

```{r}
filename <- sprintf("open_csv_%s_event_change_part_of.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```

### Event: event creation

This table details the creation event.

```{r}
filename <- sprintf("open_csv_%s_event_creation.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```

### Event: event extinction

This table details the extinction event.

```{r}
filename <- sprintf("open_csv_%s_event_extinction.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```

### Event: territory acquisition

This table details the acquisition of territory.

```{r}
filename <- sprintf("open_csv_%s_event_territory_acquisition.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```

### Event: territory acquisition

This table details the cession of territory.

```{r}
filename <- sprintf("open_csv_%s_event_territory_cession.csv", version)
dat <- read.csv(filename)
```

* file name: ``r filename``
* records: `r nrow(dat)`
* data example:

```{r}
kable(dat[sample(1:nrow(dat), 5),], row.names = FALSE)
```
